---
title: "Stat 133 Assignment 2"
author: "Xinyang Geng"
date: "January 28, 2016"
output: pdf_document
---


# 2.7
```{r, echo=FALSE, message=FALSE}
data(flights, package="nycflights13")
```
1. There are `r dim(flights)[2]` variables.

2. There are `r dim(flights)[1]` cases.

3. Each case is a flight

4. These variables are quantitive: `r names(flights)[unlist(lapply(flights[names(flights)], is.numeric))]`, 
and these are catagorical: `r names(flights)[!unlist(lapply(flights[names(flights)], is.numeric))]`

5. air_time is in minutes and distance is in miles.


# 2.8

* a. Improper syntax for function argument
* b. No assignment operator
* c. Invalid object name
* d. Unmatched quotes in character string
* e. No mistake


# 2.10
```{r, echo=FALSE, message=FALSE}
data(NCHS, package="DataComputing")
data(CountryData, package="DataComputing")
data(WorldCities, package="DataComputing")
data(BabyNames, package="DataComputing")
data(RegisteredVoters, package="DataComputing")
```

* There are `r dim(CountryData)[2]` variables.
* tfat measures mass of trunk fat
* WorldCities has `r dim(WorldCities)[1]` cases.
* The third variable in BabyNames is `r names(BabyNames)[3]`.
* The codes are `r unique(as.numeric(RegisteredVoters$party))[order(unique(as.numeric(RegisteredVoters$party)))]`.
They stand for `r levels(RegisteredVoters$party)`. 


# 3.4
* 1) BabyNames : data table name
* 2) filter : function name
* 3) name : variable name
* 4) == : function name
* 5) group_by : function name
* 6) year : variable name
* 7) sex : variable name
* 8) summarise : function name
* 9) yearlyTotal : name of a named argument
* 10) sum : function name
* 11) count : variable
* 12) ggplot : function name
* 13) aes : function name
* 14) x : name of a named argument
* 15) y : name of a named argument


# 3.5

1. The brainwt variable means: brain weight in kilograms.
2. There are totally 83 cases.
3. The real-world meaning of a case is Mammal's sleep pattern.
4. The levels are carni, omni and herbi.


# 3.6
Statement c finds average of births across all cases in each year/sex group,
instead of finding the total number of births in other statements.

# 4.1
1. \*one*: italics.
2. \*\*two**: bold font.
3. \* three: item in a bullet point list.
4. \# Four: first-level header.
5. \`five`: code font.
6. \#\# Six: second-level header.
7. \[seven](http://tiny.cc/dcf/index.html): A link with text "seven".




